---
title: "R Project 1 - Hello R"
author: "Alina Ali"
date: "9/16/2020"
output: html_document
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file have 1846 rows and 3 columns.
There are 3 variables in the data frame which includes, dataset, x, and y.

### Exercise 2

Plot `y` vs. `x` for the dino dataset. 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

To calculate the correlation coefficient between `x` and `y` for this dataset.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


Plot `y` vs. `x` for the star dataset


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

To calculate the correlation coefficient between `x` and `y` for the star dataset.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
The r value of star dataset(-0.0629611) is greater than the r value of dino dataset(-0.06447185).The r value of star and dino dataset are almost same which are negative numbers. It also shows that the relationship between x and y is not linear.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)