---
title: "R Project 1 - Hello R"
author: "Alina Ali"
date: "9/16/2020"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: pygments
    theme: readable
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```
 
 
### Exercise 1

The datasaurus_dozen file have 1846 rows and 3 columns.
There are 3 variables in the data frame which includes, dataset, x, and y.


### Exercise 2

Plot `y` vs. `x` for the dino dataset. 

```{r plot-dino, fig.height=5, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

To calculate the correlation coefficient between `x` and `y` for the dino dataset.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```


### Exercise 3

Plot `y` vs. `x` for the star dataset.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

To calculate the correlation coefficient between `x` and `y` for the star dataset.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The r value of star dataset(-0.0629611) is greater than the r value of dino dataset(-0.06447185).The r value of star and dino dataset are almost same which are negative numbers. It also shows that the relationship between x and y is not linear.


### Exercise 4

Plot `y` vs. `x` for the circle dataset.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

To calculate the correlation coefficient between `x` and `y` for the circle dataset.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The r value of circle dataset(-0.06834336) is less than the r value of dino dataset(-0.06447185).The r value of the circle and dino dataset represents negative values. In circle and dino dataset it shows that the relationship between x and y is not linear.


### Exercise 5

Plot all datasets.

```{r plot-all datasets}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

To calculate the correlation coefficient summary of all datasets.

```{r cor-group_by}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```

